---
title: "Opendata and datawarehouse ... a COVID19 machine learning tale"
author: "TF"
date: "`r Sys.Date()`"
output:
  bookdown::github_document2:
    toc: true
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r}
library(dplyr)
library(ggplot2)
library(kableExtra)
library(knitr)
library(PredictCovid)

format_kable = "pipe"

load("../../../extdata/publication_datasets/results/20220311/precompute_for_report.rdata")
```

# Objective

Sketch results section for article submission.

# Abbreviations

-   MAE : median absolute error
-   MRE : median relative error

# Results - descriptive graph

```{r variantFigure, fig.cap="Majority variant evolution by department.", fig.height=9}
# ### Import majority variant
# dfVariants <- ImportMajorityVariant() %>%
#   mutate(Majority_variant = as.character(Majority_variant)) %>%
#   rename("DATE" = "DATA_DAY") %>%
#   filter(DATE <= as.Date("2021-08-16"))
# saveRDS(object = dfVariants, file = "../../../extdata/publication_datasets/dfVariants.rds")
variantFigure

ggsave(device = "pdf", filename = "figures_pdf/FigS1_variantFigure.pdf")
```

```{r PCR, fig.cap="PCR and hospitalisations at CHU de Bordeaux. Simple moving average 7 days. Dotted line represents the maximum of hospitalisations of April peak."}
PCR

ggsave(device = "pdf", filename = "figures_pdf/Fig1_PCR.pdf")
```

During the period from `r dateStudy[1]` to `r dateStudy[2]`, `r cumNewHosp` hospitalization due to COVID19 were recorded

```{r}
dfDiagBeofreLOCF  %>%
  knitr::kable(caption = "Max number of consecutive days for LOCF imputation", format = format_kable) %>%
  kableExtra::kable_styling()
```

# Results - Analysis of the best model

Goal of second part of results is to show the predictions of the model using :

-   source = CHU only (+ Gironde data)
-   features = Open data + datawarehouse
-   smoothing span = 21 days
-   model = linear regression with elastic-net

We compute features importance and forecast predictions specifically regarding forecast delay.

## Plot prediction in delay style

```{r figDelay, fig.cap="Prediction delay according to forecast and Date", fig.height=7}
figDelay

ggsave(device = "pdf", filename = "figures_pdf/FigS2_figDelay.pdf")
```

Conclusion

-   Delay around 4 days for a 7 days forecast
-   Delay aroung 6 days for a 14 days forecast

## Plot predictions in movie style

```{r figPredMovie, fig.cap="Hospitalisation forecast each day according to different forecast time.", fig.height=4}
figPredMovie

ggsave(device = "pdf", filename = "figures_pdf/Fig3_figPredMovie.pdf")
```

Conclusion

-   Predictions are good from january to june, then they largely over estimating number of hospitalisations suggesting a vaccine effect.
-   The april decrease is too much anticipated
-   The intra-hospital cluster of december leads to wrong predictions

## EDS vs no EDS

```{r plotEDSvsNoEDS, fig.cap="Forecast depending on the use of EHR data"}
plotEDSvsNoEDS
```

# Results Bootstrap

```{r}
dfPerfBoot %>%
  filter(span == 21, model == "enet", rolderiv == "TRUE") %>%
  select(forecast, df, step, AE_median, RE_median) %>%
  mutate(step = factor(as.character(step),
                       levels = c("HospPCR",
                                  "HospPCRWeather",
                                  "HospPCRWeatherVariantsVaccine",
                                  "HospPCRGironde",
                                  "HospPCRGirondeWeather",
                                  "EDSGirondeWeather",
                                  "EDSGirondeWeatherVariantsVaccine",
                                  "EDSGirondeWeatherVariantsVaccineInterVariant",
                                  "EDSGirondeWeatherVariantsVaccineInterVaccine"),
                       labels = c("Hosp + RT-PCR",
                                  "Hosp + RT-PCR + Weather",
                                  "Hosp + RT-PCR + Weather + Variants + Vaccine",
                                  "Hosp + RT-R + Gironde Hosp + Gironde RT-PCR",
                                  "Hosp + RT-R + Gironde Hosp + Gironde RT-PCR + Weather",
                                  "Hosp + RT-R + Gironde Hosp + Gironde RT-PCR + Weather + CT-scan + emergency units + ambulance service",
                                  "Hosp + RT-R + Gironde Hosp + Gironde RT-PCR + Weather + CT-scan + emergency units + ambulance service + Variants + Vaccine",
                                  "Hosp + RT-R + Gironde Hosp + Gironde RT-PCR + Weather + CT-scan + emergency units + ambulance service + Variants + Vaccine + Variant x PCR",
                                  "Hosp + RT-R + Gironde Hosp + Gironde RT-PCR + Weather + CT-scan + emergency units + ambulance service + Variants + Vaccine + Vaccine x PCR"))) %>%
  arrange(forecast, desc(df), step) %>%
  knitr::kable(caption = "Median absolute and relative error of model predictions of Sars-Cov-2 pandemic with 95% confidence intervals. Data source evaluation.", format = format_kable) %>%
  kableExtra::kable_styling()
```

```{r}
dfPerfBoot %>%
  filter(step == "EDSGirondeWeatherVariantsVaccine", forecast %in% c(7, 14)) %>%
  select(forecast, rolderiv, span, model, AE_median, RE_median) %>%
  arrange(forecast, span, model, desc(rolderiv)) %>%
  knitr::kable(caption = "Median absolute and relative error of model predictions of Sars-Cov-2 pandemic with 95% confidence intervals. Statistical algorithm.", format = format_kable) %>%
  kableExtra::kable_styling()
```

```{r errorvalue, fig.cap="Evolution of median absolute and relative errors by month."}
errorvalue

ggsave(device = "pdf", filename = "figures_pdf/Fig5_errorvalue.pdf")
```

```{r bootPI, fig.cap="Bootstrapped prediction intervals."}
bootPI

ggsave(device = "pdf", filename = "figures_pdf/FigS3_bootPI.pdf")
```

```{r handmadePI, fig.cap="Predictions with 10% prediction intervals at 7 days and 20% at 14 days."}
plotHandmadePI
```

```{r}
dfPerfCoverage %>%
  group_by(forecast, ip, cut_date) %>%
  summarise(pct_coverage = sum(bool_inboot)/n()) %>%
  tidyr::pivot_wider(names_from = "ip", values_from = "pct_coverage") %>%
  knitr::kable(caption = "95% prediction interval coverage by bootstrap and handmade 20-40% rule. Results by time period.",
               col.names = c("Forecast day", "Period", "Bootstrap", "Handmade"),
               digits = 3, format = format_kable) %>%
  kableExtra::kable_styling()

```

```{r}
dfPerfCoverage %>%
  group_by(forecast, ip) %>%
  summarise(pct_coverage = sum(bool_inboot)/n()) %>%
  tidyr::pivot_wider(names_from = "ip", values_from = "pct_coverage") %>%
  knitr::kable(caption = "95% prediction interval coverage by bootstrap and handmade 20-40% rule",
               col.names = c("Forecast day", "Bootstrap", "Handmade"),
               digits = 3, format = format_kable) %>%
  kableExtra::kable_styling()

```

## Graph Bootstrap and EHR vs no EHR

```{r figPIEDSvsNoEDS, fig.cap="Prediction intervals and comparions EHR vs no EHR", fig.height=8}
figPIEDSvsNoEDS

ggsave(device = "pdf", filename = "figures_pdf/Fig4_figPIEDSvsNoEDS.pdf")
```

## Graph vaccine vs no vaccine data

```{r plotVaccinevsNovaccine, fig.cap="Comparions vaccine vs no vaccine data", fig.height=6}
plotVaccinevsNovaccine
```

## Features importance

```{r figImportanceCI, fig.cap="Features importance and bootstrapped confidence interval, percentage of days selecting the features in linear elastic-net model. Top 20 features are shown.", fig.height=7}
figImportanceCI

ggsave(device = "pdf", filename = "figures_pdf/Fig2_figImportanceCI.pdf")
```

```{r varimpevol7, fig.cap="Feature importance evolution. Percentage of days selecting each feature within each month. Only feature selected in every days of at least one period are displayed. 7 days forecast.", fig.height=8}
lsPlotVarImpEvol[[1]]

ggsave(device = "pdf", filename = "figures_pdf/FigS4_VarImpEvol7d.pdf")
```

```{r varimpevol14, fig.cap="Feature importance evolution. Percentage of days selecting each feature within each month. Only feature selected in every days of at least one period are displayed. 14 days forecast", fig.height=8}
lsPlotVarImpEvol[[2]]

ggsave(device = "pdf", filename = "figures_pdf/Fig6_VarImpEvol14d.pdf")
```


```{r PlotVariationVarImpUrgPed, fig.cap="Feature importance evolution. Percentage of days selecting each feature within each month. Only feature related to pediatric emergency and selected in at least 20% days of at least one period are displayed. 14 days forecast", fig.height=8}
PlotVariationVarImpUrgPed
```


